Periodograms for Multiband Astronomical Time Series

### 2015-01-30 writeup/paper.tex
fixed two typos in sec 7.1

\subsection{Comparison with \citet{Long2014}}
As we were finishing this study, it was pointed out to us that another group had released a preprint independently addressing the multiband periodogram case \citep[][hereafter LCB14]{Long2014}, and come up with a solutions very similar to the ones presented here.
They present two methods, the ``Multiband Generalized Lomb-Scargle'' (MGLS) which is effectively identical to the $(1, 0)$ multi-phase model, and the ``Penalized Generalized Lomb-Scargle'' (PGLS), which is similar in spirit to our $(0, 1)$ shared-phase model.

>>>>

\subsection{Comparison with \citet{Long2014}}
As we were finishing this study, it was pointed out to us that another group had released a preprint independently addressing the multiband periodogram case \citep[][hereafter LCB14]{Long2014}, and come up with solutions very similar to the ones presented here.
They present two methods, the ``Multiband Generalized Lomb-Scargle'' (MGLS) which is effectively identical to the $(1, 0)$ multi-phase model
here, and the ``Penalized Generalized Lomb-Scargle'' (PGLS), which is similar in spirit to our $(0, 1)$ shared-phase model.
